Parallel activation and the developing bilingual lexicon: a longitudinal study on word recognition

### 2022-02-11 presentations/2022-01-25_lacre/2022-01-25_lacre.Rmd
Relocate files

waics %>% 
	map("estimates") %>% 
	map(function(x) as.data.frame(x) %>% rownames_to_column("variable")) %>% 
	bind_rows(.id = "model") %>%
	clean_names() %>% 
	pivot_wider(names_from = variable, values_from = c(estimate, se)) %>% 
	relocate(model, matches("estimate"), matches("elpd"), matches("_p_")) %>% 
	gt() %>% 
	fmt_number(-model) %>% 
	tab_spanner("WAIC", matches("waic")) %>% 
	tab_spanner(md("WAIC<sub>ELPD</sub>"), matches("elpd")) %>% 
	tab_spanner(md("WAIC<sub>*p*</sub>"), matches("_p_")) %>% 
	cols_label(
		model = "Model",
		estimate_elpd_waic = "Estimate",
		estimate_waic = "Estimate",
		estimate_p_waic = "Estimate",
		se_elpd_waic = md("*SE*"),
		se_waic = md("*SE*"),
		se_p_waic = md("*SE*"),
	) %>% 
	as_raw_html()

>>>>

waics_l1 %>% 
	map("estimates") %>% 
	map(function(x) as.data.frame(x) %>% rownames_to_column("variable")) %>% 
	bind_rows(.id = "model") %>%
	clean_names() %>% 
	pivot_wider(names_from = variable, values_from = c(estimate, se)) %>% 
	relocate(model, matches("estimate"), matches("elpd"), matches("_p_")) %>% 
	gt() %>% 
	fmt_number(-model) %>% 
	tab_spanner("WAIC", matches("waic")) %>% 
	tab_spanner(md("WAIC<sub>ELPD</sub>"), matches("elpd")) %>% 
	tab_spanner(md("WAIC<sub>*p*</sub>"), matches("_p_")) %>% 
	cols_label(
		model = "Model",
		estimate_elpd_waic = "Estimate",
		estimate_waic = "Estimate",
		estimate_p_waic = "Estimate",
		se_elpd_waic = md("*SE*"),
		se_waic = md("*SE*"),
		se_p_waic = md("*SE*"),
	) %>% 
	as_raw_html()
